ManuscriptPURFits

### 2024-03-13 Code/Plots_PURFits.Rmd
ggsave to PlotsOutPLOS folder

#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")

@@

# ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

# geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +

@@

@@

# ggsave(file = file.path(PlotsOut, paste("BluevsRedPurFitsPlots",".tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..","Data", "CleanData")
PlotsOut <- file.path("..","Output", "Figures")
PlotsOutPLOS <- file.path("..", "OutPut", "PLOSFiguresRound1")

@@

ggsave(file = file.path(PlotsOutPLOS, "S4_Fig.tiff"), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

# geom_line(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, linetype = as.factor(Photoperiod)), size = 1, show.legend = F) +

@@

  scale_shape_manual(values = PhotoperiodShapes, labels = c("16 h", "12 h", "8 h", "4 h"))  +

@@

 ggsave(file = file.path(PlotsOutPLOS, paste("Fig9.tiff",sep = "")), plot = BluevsRedPurFitsPlots, device = NULL, scale = 1, height=40, width= 54, units = c("cm"),dpi = 300, limitsize = TRUE)
